%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage {multicol}

\begin{document}

\header{Jake}{Wernette}{Full Stack and Mobile Software Engineer} 

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
10114 Falkland Ave. Apt. 206
Raleigh NC, 27617
(989) 506-1910
~
\href{mailto:werne2@gmail.com}{werne2j@gmail.com}
\href{github.com/werne2j}{github.com/werne2j}
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------

\entry
{2011--2013}
{Computer Science{\normalfont}}
{Saginaw Valley State University}

\entry
{2013--2014}
{B.S in Computer Science{\normalfont}}
{Central Michigan University}

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2017--Present}
{IBM}
{Raleigh, North Carolina}
{\emph{Software Engineer II (Sept 2017 - Present)} \\
\emph{Software Engineer I (Jan 2015 - Sept 2017)} \\
Responsible for designing, developing, testing, and supporting strategic tools to be used in IBM's internal business from proof of concept through production.}\\

\entry
{2013--2014}
{CMU ResLife Technology Operations}
{Mt. Pleasant, Michigan}
{\emph{Web Application Developer} \\
Responsible for learning and applying best practices in front-end and back-end web development.}\\

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2016}
{Comic Collector (Not In App Store)}
{iOS - Objective-C}
{A comic book collecting iOS application. Utilizing Realm and CocoaPods.}\\

\entry
{2014}
{OneRepMax (Not In App Store)}
{iOS - Swift}
{A social networking app for power lifters to share when they get a new personal record on a specific weight lifting movement.}\\

\entry
{2013-2014}
{MyStatBook (mystatbook.com)}
{Django}
{An interactive website for baseball coaches of all levels to keep track of Rosters, Schedules and Statistics.}\\

%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	TECHNOLOGY SECTION
%----------------------------------------------------------------------------------------

\section{Technologies}

JavaScript (es6/7), Node JS, React JS, iOS Development - Objective-C/Swift, HTML, CSS, Django, Python, PostgreSQL, SQL, Vue JS, Angular JS, Backbone/Marionette JS, Git/Github, Less/Sass, Grunt/Gulp, Docker, TravisCI, CouchDB, NoSQL

\section{Hobbies}

Sports (former college baseball player), Weightlifting, Travel, Food, Comic Books, Music (Vinyl), Books
\end{document}
